Summer 2025 ToDo

### 2025-08-06 Relations/Paper/WF_diagram.tex
Diagram WFminCor WIP
WF diagram update

% Row 1: WFacc
\node[box] (WFacc) {WFacc};
\node[box, right=of WFacc] (NNWFacc) {$\lnot\lnot$WFacc};
\node[box, right=of NNWFacc] (WFaccM) {WFacc-};

\draw[arrow] (WFacc) -- (NNWFacc);
\draw[arrow] (NNWFacc) -- (WFaccM);
\draw[arrow, bend right] (WFaccM) to node[above, text=red] {accDNE} (WFacc);

@@

% Row 3: WFseq
\node[box, below=of WFacc] (WFseq) {WFseq};
\node[box, right=of WFseq] (NNWFseq) {$\lnot\lnot$WFseq};
\node[box, right=of NNWFseq] (WFseqM) {WFseq-};

\draw[arrow] (WFseq) -- (NNWFseq);
\draw[arrow] (NNWFseq) -- (WFseqM);

% Row 4: WFmin -> WFmin-
\node[box, below=of WFseq] (WFmin) {WFmin};
\node[box, right=2.8cm of WFmin] (WFminM) {WFmin-};

@@

% Row 5: WFminDNE -> WFminDNE-
\node[box, below=of WFmin] (WFminDNE) {WFminDNE};
\node[box, right=2.1cm of WFminDNE] (WFminDNEM) {WFminDNE-};

@@

\draw[arrow] (WFacc) to node[right, text = red] {Rdec} (WFseq);
\draw[arrow, bend left] (WFaccM) to (WFseqM);
\draw[arrow, bend left] (WFseqM) to node[left, text=red] {accCor} (WFaccM);  
\draw[arrow, bend left = 45] (WFaccM) to (WFminM);

@@

\draw[arrow, bend left=90] (WFminDNE) to node[left, text = red] {accDNE} (WFacc);
\draw[arrow, bend left=45] (WFminDNE) to node[pos=0.9, left, text=red] {Rdec$+$MP} (WFseq);
\draw[arrow, bend right=45] (WFminDNEM) to node[right, text=red] {FB} (WFaccM);

>>>>

% Row 1: WFacc
\node[box] (WFacc) {WFacc};
% \node[box, right=of WFacc] (NNWFacc) {$\lnot\lnot$WFacc};
\node[box, right=2.9cm of WFacc] (WFaccM) {WFacc-};

\draw[arrow] (WFacc) -- (WFaccM);
% \draw[arrow] (NNWFacc) -- (WFaccM);
\draw[arrow, bend right] (WFaccM) to node[above, text=red] {accDNE} (WFacc);

@@

% \draw[arrow] (NNWFseq) -- (WFseqM);

% Row 5: WFminDNE -> WFminDNE-
\node[box, below=of WFacc] (WFminDNE) {WFminDNE};
\node[box, right=2.0cm of WFminDNE] (WFminDNEM) {WFminDNE-};

% Row 4: WFmin -> WFmin-
\node[box, below=of WFminDNE] (WFmin) {WFmin};
\node[box, right=2.8cm of WFmin] (WFminM) {WFmin-};

@@

% Row 3: WFseq
\node[box, below=of WFmin] (WFseq) {WFseq};
% \node[box, right=of WFseq] (NNWFseq) {$\lnot\lnot$WFseq};
\node[box, right=2.9cm of WFseq] (WFseqM) {WFseq-};

\draw[arrow] (WFseq) -- (WFseqM);

% Row 6: WFcor 
\node[box, below=of WFseqM] (WFminCor) {WFminCor};

@@

\draw[arrow, bend right = 90] (WFacc) to node[left, text = red] {Rdec} (WFseq);
\draw[arrow, bend right] (WFaccM) to (WFminDNEM);
\draw[arrow, bend right = 90] (WFseqM) to node[right, text=red] {accCor} (WFaccM);  
% \draw[arrow, bend left = 55] (WFaccM) to (WFminM);

@@

\draw[arrow] (WFminDNE) to node[left, text = red] {accDNE} (WFacc);
\draw[arrow, bend right=45] (WFminDNE) to node[pos=0.5, left, text=red] {MP$\equiv$} (WFseq);
\draw[arrow, bend right] (WFminDNEM) to node[right, text=red] {FB} (WFaccM);
\draw[arrow, bend right] (WFseqM) to (WFminCor);
\draw[arrow, bend right] (WFminCor) to node [right, text=red] {MP$\equiv$} (WFseqM);
